Helixer: Cross-species gene annotation of large eucaryotic genomes using deep learning

### 2020-04-22 paper/main.tex
minor
supplements started in extra file

\subtitle{Really cool deep learning stuff}

\title[short Title]{General purpose gene annotation using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

\section{Conclusion}
We propose a gene calling model that is able to perform cross-species genomic annotiation for a wide variety of large eucaryotic genomes. Our model does this while outperforming AUGUSTUS on a base pair wise level and withstanding RNASeq data based scrutiny.

>>>>

\subtitle{Genome analysis}

\title[short Title]{Helixer: Cross-species gene annotation of large eucaryotic genomes using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Stephan Scholz, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

\section{Discussion}
We propose a gene calling model that is able to perform cross-species genomic annotiation for a wide variety of large eucaryotic genomes. Our model does this while outperforming AUGUSTUS on a base pair wise level and withstanding RNASeq data based scrutiny.
